All Your Graphs Belong to Us

### 2012-07-19 doc/asplos13/method.tex
description of systems PAL and XMT

@@

\paragraph{Unbalanced tree search (UTS)}, is a benchmark for evaluating the programmability and performance of systems for parallel applications that require dynamic load balancing \cite{Olivier:uts2006}. It involves traversing an unbalanced implicit tree: at each vertex, its number of children is sampled from some probability distribution, and this number of new nodes are added to a work queue to be visited. While this benchmark captures irregular, dynamic parallelism, we want to evaluate performance on algorithms that touch existing data. We augment UTS by using the traversal to create a large tree in memory, and then we traverse the in-memory tree. We call this benchmark UTS-mem, and the timed portion is this traversal of the in-memory tree. The assumption is that in general the size of each subtree is unknown until that subtree has actually been traversed.

>>>>

\subsection{Systems}
For measurements, we run Grappa on a 144-node cluster of AMD
Interlagos processors, located at Pacific Northwest National Lab
(PNNL). Nodes have 32 core (every pair share a floating-point
unit) 2.1-GHz processors, and 64GB of memory, and \TODO{xxx 40Gb network card}. \todo{cluster
    uses xxx Infiniband switch}. We configure the nodes to have 32 1-GB
hugepages to minimize TLB misses for the random access patterns we
expect from irregular applications. The results we present are for
this machine, but we have also run Grappa on our own 12-node Intel
Xeon Westmere cluster.

For the MTA comparison, we use a 128-node Cray XMT (3rd generation
of the MTA), also located at PNNL. Each node consists of a 500-MHz MTA Threadstorm multithreaded
processor that supports 128 streams. The machine uses Cray's proprietary
SeaStar2 interconnection network.

@@

\paragraph{Unbalanced tree search in-memory (UTS-Mem)}, is a benchmark
for evaluating the programmability and performance of systems for
parallel applications that require dynamic load balancing
\cite{Olivier:uts2006}. It involves traversing an unbalanced implicit
tree: at each vertex, its number of children is sampled from some
probability distribution, and this number of new nodes are added to a
work queue to be visited. While this benchmark captures irregular,
dynamic parallelism, we want to evaluate performance on algorithms
that touch existing data. We augment UTS by using the traversal to
create a large tree in memory, and then we traverse the in-memory
tree. We call this benchmark UTS-Mem, and the timed portion is this traversal of the in-memory tree. The assumption is that in general the size of each subtree is unknown until that subtree has actually been traversed.
